%-------------------------------------------------------------------------------
%	HEADERS
%-------------------------------------------------------------------------------
\vspace{20mm}
%\lettertitlestyle{Job Application for Senior Devops Engineer}
\vspace{10mm}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cvletter}

Dears,

I am thrilled to offer my services to help you with your firm’s upcoming challenges, in business and technology, as I would love to leverage my excelled education in MBA and computer engineering, versatile knowledge within the past 10 years of discipline and passion for information systems and solutions. I have experience in leading successful cross-functional teams, and carefully managing IT aspects with advanced top-notch technology trends.

Throughout my career, I've helped my firm in seeking and forming new technologies into viable business opportunities while assuring our systems’ scalability, security, and elasticity. Wearing multiple hats as IT personnel in systems administration, DevOps practices, AWS cloud computing, and project management. Being responsible for whole systems, services, CI/CD pipelines, products' releases, projects' delivery, API gateway, IT procurement and recruitment, team leadership, clients' interaction, and CTO tasks.

During the past 7 years of my duty with Souktel Inc, I've stacked up several operational technologies and activities to facilitate the firm's rapid growth as a startup, introducing DevOps practices as of CI/CD pipeline toolchain, central logging on ELK, Prometheus monitoring and Slack/email alerting, adding new services like RabbitMQ and Keycloak for microservices architecture, through Dockerized structure on Swarm. Exercising infrastructure and configuration as code through Jenkins DSL, Bash/Python scripts, Ansible and CloudFormation.

My current focus carries everything-as-code and Kubernetes as keystones of successful DevOps, and hence the overall business.

I welcome the chance to discuss your business and technology objectives and present my proven skillset in translating those into achievable action plans and effective strategical roadmap.

Sincerely,

Thabet
\end{cvletter}

