%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps Manager} % Job title
    {Souktel Inc} % Organization
    {USA} % Location
    {since Jan ’18} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Led the process of elevating development processes efficiency and overall SDLC, through implementing DevOps practices that turned to save 30\% of software release time by initiating CI/CD with Jenkins, Docker, Swarm, Ant with Sahi for test automation. Pioneered infrastructure and configurations as code toolsets with CloudFormation, Terraform and Ansible to ease managing 30+ AWS EC2s, introducing central logging to ELK stack and monitoring on Prometheus stack with alerts sent to Slack and email.\\
        To promote the firm's DevOps adoption, I've trained the development team and headed migrating of the production environment and setting policies for the releasing process. Redesigned the infrastructure to serve a microservices-driven architecture, including RabbitMQ and KeyCloak as local services.}
      \end{cvitems}
    }

\cventry
    {Integration Lead Engineer} % Job title
    {Souktel Inc} % Organization
    {USA} % Location
    {Feb ’13 - Dec ’17} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Besides the daily routine system administration duties on AWS and light loads on Azure and GCP, I led 10+ Agile software projects using Kanban and Scrum, with 10s-100s K USD budgets as SaaS platforms for data collection, ME, Outreach, and LMS, using CodeIgniter and Laravel frameworks, MySQL, MongoDB, JIRA, BitBucket Git. Moreover, I designed, developed and maintained REST APIs based on PHP and Python for various telecom and social channels.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator And Architect} % Job title
    {UN Office on Drugs and Crime} % Organization
    {Palestine} % Location
    {Nov ’12 - Oct ’13 (1yr)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Was assigned as an IT program consultant to help a local governmental department in the design and building a highly-available mail system, serving 1K+ users, scalable to 10K+, integrated with LDAP for AAA, based on Linux, Postfix, Dovecot, and Roundcube. To sustain the project, I trained a 15+ IT operations team and introduced ISO-9001 SOP for technical documentation using Wiki.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Networks And Systems Engineer} % Job title
    {Bisan Systems Ltd} % Organization
    {Palestine} % Location
    {Nov ’10 - Oct ’12 (2yrs)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Directed the process of migrating the system to poly-cloud IaaS providers like Amazon AWS, Alongside managing multi-location hybrid datacenters. Also, I administered business applications backed by replicated MySQL databases and employed advanced monitoring, performance graphing and alarming alerts with Nagios/Cacti/SNMP/Asterisk.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems And VoIP Solutions Engineer} % Job title
    {Exalt Technologies Ltd} % Organization
    {Palestine} % Location
    {Feb ’09 - Oct ’10 (21mos)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Helped in entering the VoIP market by designing commercial Asterisk SIP/IAX IP-PBX and eFax solution, besides system administration duties for local network, on-premise Linux servers, and various open-source software as OpenVPN, LDAP/RADIUS, Twiki, Bugzilla, Trac, SVN, Bind, Squid, and Samba.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
