%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvgroupentry
    {Souktel Inc} % Organization
    {USA} % Location
    {since Feb ’13 (7yrs)} % Date(s)

  \cvposentry
    {Deputy CTO} % Job title
    {since Oct ’18} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Through proven technical and leadership skills, I was promoted to take over CTO’s daily operational duties, by overseeing 5+ concurrent agile software projects’ delivery, leading a cross-functional team of 20+ engineers to ensure completion of deliverables and adherence to timelines, conducting recruiting and training for staff and resource planning, among with practicing DevOps and cloud operations.}
      \end{cvitems}
    }

  \cvposentry
    {Development Operations Manager} % Job title
    {since Jan ’18} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Led the process of elevating development processes efficiency and overall SDLC, through implementing DevOps practices that turned to save 30\% of software release time by initiating CI/CD with Jenkins, Docker, Swarm, Ant with Sahi for test automation. Pioneered Infrastructure as Code toolsets with CloudFormation and Ansible to ease managing 30+ AWS EC2s.}
      \end{cvitems}
    }

\cvposentry
    {Integration Lead Engineer} % Job title
    {Feb ’13 - Dec ’17} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Besides the daily routine system administration duties on AWS and light loads on Azure and GCP, I led 10+ Agile software projects using Kanban and Scrum, with 10s-100s K USD budgets as SaaS platforms for data collection, ME, Outreach, and LMS, using CodeIgniter and Laravel frameworks, MySQL, MongoDB, JIRA, BitBucket Git. Moreover, I designed, developed and maintained REST APIs based on PHP and Python for various telecom and social channels.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {System Administrator And Architect} % Job title
    {UN Office on Drugs and Crime} % Organization
    {Palestine} % Location
    {Nov ’12 - Oct ’13 (1yr)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Was assigned as an IT program consultant to help a local governmental department in the design and building a highly-available mail system, serving 1K+ users, scalable to 10K+, integrated with LDAP for AAA, based on Linux, Postfix, Dovecot, and Roundcube. To sustain the project, I trained a 15+ IT operations team and introduced ISO-9001 SOP for technical documentation using Wiki.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Networks And Systems Engineer} % Job title
    {Bisan Systems Ltd} % Organization
    {Palestine} % Location
    {Nov ’10 - Oct ’12 (2yrs)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Directed the process of migrating the system to poly-cloud IaaS providers like Amazon AWS, Alongside managing multi-location hybrid datacenters. Also, I administered business applications backed by replicated MySQL databases and employed advanced monitoring, performance graphing and alarming alerts with Nagios/Cacti/SNMP/Asterisk.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems And VoIP Solutions Engineer} % Job title
    {Exalt Technologies Ltd} % Organization
    {Palestine} % Location
    {Feb ’09 - Oct ’10 (21mos)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        {Helped in entering the VoIP market by designing commercial Asterisk SIP/IAX IP-PBX and eFax solution, besides system administration duties for local network, on-premise Linux servers, and various open-source software as OpenVPN, LDAP/RADIUS, Twiki, Bugzilla, Trac, SVN, Bind, Squid, and Samba.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
